Out-of-Sample Comparisons of Overfit Models

### 2016-01-31 paper.tex
[#51] Switch BibTeX database to latex-tools version
This switch adds records for a few papers and (probably more important)
updates the records of a few of my papers in the BibTeX database. The
bibtex keys change for those papers, so the files need to be updated
in the LaTeX files as well.

\documentclass[12pt]{article}
\input{setup}

@@

\citet{GoW:08} focus primarily on univariate regression models of the
form
\[
r_{t+1} = \beta_0 + \beta_1 x_{it} + \e_{t+1}
\]
using OLS with a recursive window, where $r_{t+1}$ is the equity
premium and $x_{it}$ is one of the predictors listed in
Table~\ref{tab:equity}.
This focus is consistent with much of the rest of the literature. But
it is not clear that this approach---using a large number of
restricted models---is any more reliable than using a single, large
model. Very few papers in the equity-premium predictability literature
explicitly account for the multiplicity of model comparisons%
\footnote{\citet{RaW:06}, \citet{RaZ:12}, and \citet{Cal:13b} are
  exceptions.} %
and most widely-used statistics for multiple comparisons are
derived under the assumption that there is a finite number of
hypotheses or models (as is the case in \citealp{STW:99c},
\citealp{Whi:00}, \citealp{Han:05}, and \citealp{LeR:05}), so there is
little theoretical evidence that they are any more reliable than a
regression model that encompasses all of the smaller models. Moreover,
since \citet{GoW:08} (along with most of the rest of the literature)
want to interpret these univariate regressions as meaningful
statements about the true relationships between the equity premium and
the regressors, omitted variable bias is a serious potential issue.

@@

\bibliographystyle{abbrvnat}
\bibliography{references}

>>>>

\documentclass[12pt,draft]{article}
\input{VERSION}
\input{setup}

@@

\citet{GoW:08} focus primarily on univariate regression models of the
form
\[
r_{t+1} = \beta_0 + \beta_1 x_{it} + \e_{t+1}
\]
using OLS with a recursive window, where $r_{t+1}$ is the equity
premium and $x_{it}$ is one of the predictors listed in
Table~\ref{tab:equity}.
This focus is consistent with much of the rest of the literature. But
it is not clear that this approach---using a large number of
restricted models---is any more reliable than using a single, large
model. Very few papers in the equity-premium predictability literature
explicitly account for the multiplicity of model comparisons%
\footnote{\citet{RaW:06}, \citet{RaZ:12}, and \citet{Cal:15} are
  exceptions.} %
and most widely-used statistics for multiple comparisons are
derived under the assumption that there is a finite number of
hypotheses or models (as is the case in \citealp{STW:99c},
\citealp{Whi:00}, \citealp{Han:05}, and \citealp{LeR:05}), so there is
little theoretical evidence that they are any more reliable than a
regression model that encompasses all of the smaller models. Moreover,
since \citet{GoW:08} (along with most of the rest of the literature)
want to interpret these univariate regressions as meaningful
statements about the true relationships between the equity premium and
the regressors, omitted variable bias is a serious potential issue.

@@

\bibliographystyle{abbrvnat}
\bibliography{latex-tools-0.2.1/references}
